Temporal stability in human interaction networks: sector sizes, topological prominence and time activity

### 2015-10-03 paper.tex
adicionada referencia ao ccs
arrumado resumo

\begin{abstract}
In this study we demonstrate a remarkably stable activity in human interaction networks. The activity along time and topology evolution were investigated in email lists by considering window sizes from 50 to 10,000 messages, which were made to slide and generate snapshots of the network in a timeline. Notably, the activity in timescales, ranging from seconds to months, is practically the same for all lists. The activity of participants followed the expected scale-free behavior, thus allowing us to establish three classes of vertices by comparing against the Erd\"os-R\'enyi model, namely hubs, intermediary and peripheral vertices. The relative size of these three sectors did not vary with time and was essentially the same for all email lists. Typically, 3-12\% of the vertices are hubs, 15-45\% are intermediary and the remainder are peripheral vertices. The metrics that contribute most to the dispersion of participants in the topological measures space are centrality measurements (degree, strength and betweenness), followed by symmetry-related metrics and then clustering coefficient. Similar results for the distribution of participants in the three categories and for the relative importance of the topological metrics were obtained for 12 additional networks from Facebook, Twitter and Participa.br. Consistent with expectations from the literature, these properties may be general for human interaction networks, which has important implications in establishing a typology based on objective, quantitative criteria.
\end{abstract}

@@

Data from social networks used in this study were gathered and used within the anthropological physics framework~\cite{anPhy}.
All data used are also publicly accessible, either because they were already in public domain or because
we published our own annotations.
Messages were downloaded from the GMANE public database~\cite{GMANEwikipedia}.
Data annotated from Facebook and Twitter are in a public repository~\cite{fbtwData}.
Data from Participa.br was used from the linked data/semantic web RDF triples
reported in~\cite{opa} and available in~\cite{datahub}.

>>>>

\begin{abstract}
In this study we report on stable aspects of human interaction networks,
with benchmarks derived from public email lists.
Activity along time and topology evolution were observed by snapshots in a timeline 
and in various scales.
Notably, the activity in timescales, ranging from seconds to months, is practically the same for all networks.
The most important metrics to the dispersion of participants in the topological measures space 
are centrality measurements (degree, strength and betweenness),
followed by symmetry-related metrics and then clustering coefficient.
The activity of participants followed the expected scale-free trace,
thus yielding three classes of vertices by comparison against the Erd\"os-R\'enyi model,
namely hubs, intermediary and periphery.
The relative size of these three sectors did not vary with time and was essentially the same for all email lists.
Typically, 3-12\% of the vertices are hubs, 15-45\% are intermediary and the remainder are peripheral vertices.
Similar results for the distribution of participants in the three categories and for the relative importance of the topological metrics were obtained for 12 additional networks from Facebook, Twitter and Participa.br. Consistent with expectations from the literature, these properties may be general for human interaction networks, which has important implications in establishing a typology based on quantitative criteria.
\end{abstract}

@@

Data from social networks used in this study were gathered and used within the anthropological physics framework~\cite{anPhy,ccs15}.
All data used are also publicly accessible, either because they were already in public domain or because
we published our own annotations.
Messages were downloaded from the GMANE public database~\cite{GMANEwikipedia}.
Data annotated from Facebook and Twitter are in a public repository~\cite{fbtwData}.
Data from Participa.br was used from the linked data/semantic web RDF triples
reported in~\cite{opa} and available in~\cite{datahub}.
